\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Nageswara Rao}{Maridu}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{ Staff Software Engineer}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +1 587-969-9556& \enspace\faEnvelope\enspace maridu.nageswararao@gmail.com& \enspace\faHome\enspace Calgary, Canada\\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ c c }
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/nrmaridu/}{in/nrmaridu} &
\enspace \faGithub\enspace \color{blue} \href{https://github.com/????}{github.com/nrmaridu}
\end{tabular}
\end{center}

\section{Profile}
{Results-oriented and innovative Senior Software Engineer with 9+ years of
experience in building large scale cloud native SaaS applications.
Responsible and articulate individual with strengths in solutions optimization,
cloud, SaaS solutions and project management.}

\section{Areas of Expertise}
{Software Development - Distributed Systems - Microservices - Cloud Computing - Object Oriented Design - Concurrent Programming - REST - Event Driven Architecture - IAM - DDD - TDD - Campaign Management - Lead Generation}

\section{Professional Experience}
\customcventry{06/2023 ‐ present}{{\color{blue}\href{https://google.com/}{(Stellar Systems)}}}{Digital Marketing Strategist,}{Las Vegas, NV}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed strategic plans for campaigns across email, social media, SEO/SEM, and display advertising techniques.
\item Developed and implemented digital marketing strategies that generated over \$850,000 in revenue in 2023
\item Oversee the execution of SEO, SEM, email, social media, and display advertising campaigns, achieving a 12\% decrease in cost per acquisition
\end{itemize}}}

\customcventry{01/2023 ‐ 05/2023}{{\color{blue}\href{https://www.google.com/}{(Synapse Solutions)}}}{Digital Account Manager,}{Las Vegas, NV}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Implemented promotional activities such as re-targeting campaigns for e-commerce businesses.
\item Monitored the performance of PPC campaigns through Google Adwords. 
\item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates
\end{itemize}}}

\customcventry{03/2023 ‐ 12/2023}{{\color{blue}\href{https://www.google.com/}{(CeeCee Marketing)}}}{Marketing Coordinator,}{New YOrk, NY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Identified and executed improvements for processes, content, and lead generation.
\item Collaborated with Content Team to promote blog posts and guest posts.
\item Implemented new competitive analysis and consumer trend reports to increase quarterly sales by 15%.
\end{itemize}}}

\customcventry{01/2022 ‐ 07/2022}{{\color{blue}\href{https://www.google.com/}{(Some Icon, LLC)}}}{Executive Assistant,}{New York, NY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Identified new autoposting solution to cut social media time spent by 35%.
\item Prepared written text proposals and speech writing drafts.
\item Managed all public social media profiles of important public figure.
\end{itemize}}}

\customcventry{06/2021 ‐ 12/2021}{{\color{blue}\href{https://www.google.com/}{(Main Company)}}}{Digital marketer,}{New York, NY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Reached 120\% of customer acquisition target, capturing 7,500 new subscribers in six months following development and launch of a niche-marketing campaign.
\item Facilitated a medical-billing company's domination of the Northeast market with successful PR initiatives.
\end{itemize}}}

\customcventry{01/2021 ‐ 06/2021}{{\color{blue}\href{https://www.google.com/}{(Something Company)}}}{Digital Marketing Specialist,}{Seattle , USA}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed and led processes to expand retail opportunities, and facilitated client on-boarding.
\item Brought forth a strong understanding of SEO best practices, and developed and implemented SEO strategies.
\item Managed the marketing database and data management initiatives.
\end{itemize}}}

\customcventry{01/2019 ‐ 01/2021}{{\color{blue}\href{https://www.google.com/}{(ABC Marketing Agency)}}}{Digital Marketing Specialist,}{Seattle , USA}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Defined, developed, and implemented marketing strategies to automate and measure target audience movement.
\item Led 3 premium projects with a team of 3 members
\item Increased client website impressions by 0-20K through SEO strategies in 12 months and boosted organic traffic by 10\%
\item Established processes and protocols for campaign measurement to optimize results.
\end{itemize}}}

\customcventry{01/2018 ‐ 12/2018}{{{Freelancer}}}{Digital Marketing Intern,}{Seattle , USA}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates
\item Achieved a 23\% increase in conversion rates by conducting A/B testing and analyzing data to improve website performance.
\end{itemize}}}

\section{Online Courses \& Certifications}
{\begin{itemize}[label=\textbullet]
      \item Introduction to Digital Marketing (Jan. 2023) - \underline{\color{blue}\href{https://google.com/}{SEMRUSH}}
      \item Career Essentials in Digital Marketing by LinkedIn (Aug. 2022) - \underline{\color{blue}\href{https://google.com/}{LinkedIn}}
      \item Visualization with Tableau (Feb. 2022) - \underline{\color{blue}\href{https://google.com/}{Coursera}}
      \item Foundations of Google Analytics  (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google, Coursera}}
     \item Google Analytics for Power Users (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google}}
       \item The Fundamentals of Digital Marketing, (Jul. 2019) - \underline{\color{blue}\href{https://google.com/}{Google}} 
  \end{itemize}} 

\section{Education}
\customcventry{2008-2014}{\color{blue}\href{https://www.google.com/}{Rajiv Gandhi University of Knowledge Technologies}}{Integrated Dual Degree}{Nuzvid, India}{}{}{Relevant Courses: Bachelor of Technology in Computer Science \& Engineering | Minor degree in Business Management.}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Data Visualization:} Microsoft Power BI, Excel}
\item {\textbf{Digital Marketing:} Project Management, Social Media Optimization, Content Writing, Campaign Analysis \& Reporting, PPC \& SEM Strategies, Conversion rate optimization (CRO), PPC advertising}
\item {\textbf{Software:} Project (MSP), Adobe PhotoShop, Audition, Canva}
\item {\textbf{SEO:} Google Search Console, Analytics, Looker Studio, Trends, Screaming Frog, SEMrush, Ahrefs, WordPress}
\item {\textbf{Soft Skills:} Presentation, Planning, Organized, Creative Problem-Solving, Teamwork, Active Listening, Adaptability, Analytical Thinking}
\end{itemize}}

\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{Telugu} [Native]
    \item \textbf{English} [Professional]
    \end{itemize}
\end{multicols}
\end{document}
